Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-08-10 paper.tex
Update paper.tex

Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role. For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015}); introgression has conferred M\"{u}llerian mimicry \mbh{I would explain a bit more here...wing coloration loci, protects against predation...} across butterfly species \cite{Heliconius2012}; introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}.

>>>>

Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role.
For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015});
introgression of wing coloration loci has conferred M\"{u}llerian mimicry
(a type of mimicry in which two unpalatable species resemble one another, compounding the efficacy of their repellant signal)
%\mbh{I would explain a bit more here...wing coloration loci, protects against predation...}
across butterfly species \cite{Heliconius2012}; introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}.
